=enter title here=

### 2021-07-25 paper/agujournaltemplate.tex
Write synthetics part

Example: Synthetics

>>>>

To illustrate the wavelet transform method, we first apply the MODWT to synthetics data. As slow slip events occur in Cascadia on a regular basis, every twelve to eighteen months, we create a synthetic signal of period $T = 500$ days. To reproduce the ground displacement observed on the longitudinal component of GPS stations in Cascadia, we divide each period into two parts: In the first part of duration $T - N$, the displacement is linearly increasing and corresponds to the secular plate motion in the eastern direction; in the second part of duration $N$, the displacement is linearly decreasing and corresponds to a slow slip event on a reverse fault at depth triggering a ground displacement in the western direction. To see the effect of the magnitude of the slow slip event, we use different values for $N = 2, 5, 10, 20$ days. Figure X shows the synthetics, the details of the wavelet decomposition for levels 1 to 8, and the smooth for the four durations of a slow slip event. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={5cm 6cm 5cm 9cm},clip]{figures/500_DS.pdf}
\caption{Details and smooth of the wavelet decomposition of a synthetics signal with period 500 days and duration of the slow slip event equal to 2 days (left), 5 days, 10 days, and 20 days (right).}
\label{pngfiguresample}
\end{figure}

The ramp-like signal is transformed through the wavelet filtering into a waveform with first a positive peak and then a negative peak. The width of the waveform increases with the scale level. For the 8th level of the wavelet decomposition, the width of the waveform is nearly as large as the time between two events. We do not show details at larger scales as the corresponding waveforms would start to merge two contiguous events together, and make the wavelet decomposition less interpretable. For an event of duration 2 days, the wavelet details at levels higher than 2 have a larger amplitude than the wavelet detail at level 1. For an event of duration 5 days, the wavelet details at levels higher than 3 have a larger amplitude than the wavelet details at lower scales. For an event of duration 10 days, the wavelet details at levels higher than 5 have a larger amplitude than the wavelet details at lower scales. For an event of duration 20 days, the wavelet details at levels higher than 6 have a larger amplitude than the wavelet details at lower scales. Thus, the scale levels at which an event is being seen in the wavelet details give us an indication about the duration (and the magnitude) of the slow slip event. We expect the big slow slip events of magnitude 6-7 that lasts about 10 days to start being visible at the level 5 of the wavelet decomposition, but to not be noticeable at lower time scales. \\
